---
title: "R Table HTML"
output:
  html_document:
    keep_md: true
---

```{r comment='', message=FALSE, warning=FALSE}
library("stargazer")
library("dplyr")
library("nycflights13")
library("AER") # Applied Econometrics with R
```

```{r comment='', message=FALSE, warning=FALSE}
daily <- flights %>%
  filter(origin == "EWR") %>%
  group_by(year, month, day) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE))

daily_weather <- weather %>%
  filter(origin == "EWR") %>%
  group_by(year, month, day) %>%
  summarise(temp   = mean(temp, na.rm = TRUE),
            wind   = mean(wind_speed, na.rm = TRUE),
            precip = sum(precip, na.rm = TRUE))

# Merge flights with weather data frames
both <- inner_join(daily, daily_weather) %>% 
  data.frame()  # Temporary fix

# Create an indicator for quarter
both$quarter <- cut(both$month, breaks = c(0, 3, 6, 9, 12), 
                                labels = c("1", "2", "3", "4"))

# Create a vector of class logical
both$hot <- as.logical(both$temp > 85)

head(both)
```

# The default summary statistics table

```{r comment='', message=FALSE, warning=FALSE, results='asis'}
stargazer(both, type = "html")
```

When supplied a data frame, by default stargazer creates a table with summary statistics. If the **summary** option is set to FALSE then stargazer will instead print the contents of the data frame. 

```{r comment='', message=FALSE, warning=FALSE,results='asis'}
# Use only a few rows
both2 <- both %>% slice(1:6)
stargazer(both2, type = "html", summary = FALSE, rownames = FALSE)
```

# Change which statistics are displayed

In order to customize which summary statistics are displayed, change any of the the following (logical) parameters, `nobs`, `mean.sd`, `min.max`, `median`, and `iqr`.  

```{r comment='', message=FALSE, warning=FALSE, results='asis'}
stargazer(both, type = "html", nobs = FALSE, mean.sd = TRUE, median = TRUE, iqr = TRUE)
```

# Change which statistics are displayed (a second way)

```{r comment='', message=FALSE, warning=FALSE, results='asis'}
stargazer(both, type = "html", summary.stat = c("n", "p75", "sd"))
```

# Remove logical variables in the summary statistics

```{r comment='', message=FALSE, warning=FALSE, results='asis'}
stargazer(both, type = "html", summary.logical = FALSE)
```

# Flip the table axes

```{r comment='', message=FALSE, warning=FALSE, results='asis'}
stargazer(both, type = "html", flip = TRUE)
```

# Control the number of decimal places

```{r comment='', message=FALSE, warning=FALSE, results='asis'}
stargazer(both, type = "html", flip=TRUE, digits = 1)
```

# Drop leading zeros from decimals

```{r comment='', message=FALSE, warning=FALSE, results='asis'}
stargazer(both, type = "html", flip=TRUE, digits = 1, initial.zero = FALSE)
```

